\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-10 Manuscript/Manuscript.tex
Added background section and edited intro and formatting

\if0\blind
{
  \title{\bf Manuscript Draft}
  \author{Zoe Macris}
\date{December 2023}
  \maketitle}

@@

For being around for just over 200 years, the bicycle has constantly evolved in it's utility to us as a society. Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}. It is an excellent for of exercises for our increasingly sedentary society, giving a cardio workout that improves flexibility and isn't hard on the joints. It also can help people's mental health as well as physical. Beyond these individual benefits, cycling has a benefit for the environment and society as a whole It is a sustainable mode of transportation, not releasing any carbon emissions and requiring much less infrastructure and parking than automobiles. It is because of these benefits, that investing time and resources into cycling infrastructure is important. Bike lanes, separated paths and bike-friendly intersections can all be used to encourage cycling, leading to the benefits of improved public health and air quality, as well as making it a safe activity for those who chose to cycle. Additionally, cycling is only a viable option for some individuals with disabilities or limited mobility when there is proper cycling infrastructure. This is where statistics comes in. In order to reap these benefits of cycling, we can analyse data to promote cycling infrastructure to decision makers.

@@

\begin{table}[tbp]
\label{fig:Mateo-Babiano}
\centering
\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
\begin{tabular}{l*{5}{p{2cm}}}
\toprule
{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
\midrule
Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\if0\blind
{
  \title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
  \author{Zoe Macris}
\date{December 2023}
  \maketitle}

@@

Given that they have been around for just over 200 years, the bicycle has  evolved considerably in it's utility to us as a society. Originally just for hobbyists, and inhibitively expensive, they are now one of the most accessible modes of transport \cite{BIKE2023}. The World Health Organizations recommendation is a minimum of 150 minutes of moderate aerobic activity per week (WHO, 2021). This is difficult to achieve in our sedentary society, but cycling is an excellent form of exercise that can also double as the mode of transport for commuting and completing daily tasks. Furthermore, getting the appropriate amount of exercise can have an estimated risk reduction of 30\% for all-cause mortality, including from cardiovascular disease, coronary heart disease, stroke, diabetes and cancer. (Gotschi, 2014). It also can help people's mental health as well as physical, some studies have even demonstrated a decrease in depression symptoms from cycling for transportation (NIH, 2021). Beyond these individual benefits, cycling has a benefit for the environment and society as a whole. Transportation is a large source of greenhouse gas emissions for many countries (NIH, 2021). In recent years, there has been even more emphasis on sustainable and environmentally conscious transportation options in urban areas.  Cycling fits the these criteria and has risen to prominence as a viable sustainable mode of transportation. It is a form of active transportation, which is defined as human powered, and thus does not release greenhouse gas emissions. Bikes also take up considerable less space and require significantly less infrastructure than cars as an added benefit. In order to promote cycling and make use of the benefits of alleviating traffic congestion, reduced emissions, and enhancing public health, it has become necessary to plan and evaluate cycling infrastructure, and bike lanes more specifically. Statistical research and analysis on bike lanes provides crucial insights into the usage patterns, attitudes, commute rates, bicycle traffic and safety. This survey paper aims to provide an comprehensive examination of the existing body of statistical research into bike lines. With this, we hope to show trends in the research, give an overview of statistical findings and identify areas that can be further developed.

\section{Background}
\label{sec:Background}

@@

\begin{table}[tbp]
\small
\label{fig:Mateo-Babiano}
\centering
\caption{Length of bikeway by bikeway type in Brisbane and CityCycle areas. Spearman correlation of station usage and infrastructure type: from Mateo-Babiano paper}
\begin{tabular}{l*{5}{p{1.5cm}}}
\toprule
{Infrastructure type} & {Length Brisbane Area (km)} & {Lenth in CityCycle area (km)} & {Correlation coefficent} & {P-value}\\
\midrule
Shared Pathway & 327.9 & 18.0 & 0.42 & <0.01 \\
Bicycle Lane & 186.7 & 21.3 & 0.03 & 0.69 \\
Bicycle Awareness Zone (BAZ) & 303.7 & 40.3 & -0.07 & 0.39 \\
Bicycle Path & 23.9 & 2.6 & 0.27 & <0.01 \\
Bicycle Route (BAZ) & 76.9 & 8.2 & 0.13 & 0.11 \\
Connect & 19.5 & 5.0 & 0.16 & 0.049 \\
Informal Off Road & 65.8 & 4.6 & 0.00 & 0.98 \\
Informal On Road & 18.2 & 4.1 & -0.13 & 0.12 \\
Separated Pathway & 1.8 & 1.3 & 0.29 & <0.0 \\
\bottomrule
\end{tabular}
\end{table}
